07_DESeq_ALL

### 2019-04-15 analysis/07_DESeq2_ALL.Rmd
recent updates

---
title: "05_DESeq_manipulation"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/manipulation/',cache=TRUE)

```

# Manipulation data

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
m.colData <- read.csv("../results/00_colData_manipluation.csv", header = T, row.names = 1)
m.countData <- read.csv("../results/00_countData_manipluation.csv", header = T, row.names = 1)
geneinfo <- read.csv("../results/00_geneinfo.csv", row.names = 1)

# set levels
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("m.inc.d3", "m.inc.d8", "m.inc.d9",
                                "m.inc.d17",  "prolong", "extend", "m.n2"))

m.colData$sextissue <- as.factor(paste(m.colData$sex, m.colData$tissue, sep = "_"))
```

# Write for loop to do this one for every tissue and for every treatment

```{r althings}
for (eachgroup in levels(m.colData$sextissue)){

@@

  colData <- m.colData %>%
      dplyr::filter(sextissue == eachgroup) %>%
      droplevels()
  row.names(colData) <- colData$V1

@@

  countData <- m.countData %>% dplyr::select(one_of(savecols))

@@

dat$V1 <- factor(dat$V1, levels = 
                              c("m.inc.d3", "m.inc.d8", "m.inc.d9",
                                "m.inc.d17",  "prolong", "extend", "m.n2"))
dat$V2 <- factor(dat$V2, levels = 
                              c("m.inc.d3", "m.inc.d8", "m.inc.d9",
                                "m.inc.d17",  "prolong", "extend", "m.n2"))

>>>>

---
title: "07_DESeq_ALL"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/ALL/',cache=TRUE)
```

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
m.colData <- read.csv("../results/00_colData_manipluation.csv", header = T, row.names = 1)
m.countData <- read.csv("../results/00_countData_manipluation.csv", header = T, row.names = 1)

c.colData <- read.csv("../results/00_colData_characterization.csv", header = T, row.names = 1)
c.countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)

a.colData <- rbind(m.colData, c.colData)
a.countData <- cbind(m.countData, c.countData)

a.colData$sextissue <- as.factor(paste(a.colData$sex, a.colData$tissue, sep = "_"))
```

```{r factors} 
a.colData$treatment <- factor(a.colData$treatment, levels = 
                              c("control", "bldg", "lay", "inc.d3", "inc.d9", 
                                "inc.d17", "hatch", "n5", "n9",
                                "m.inc.d3", "m.inc.d8", "m.inc.d9",
                                "m.inc.d17",  "prolong", "extend", "m.n2"))
```

```{r althings}

for (eachgroup in levels(a.colData$sextissue)){

@@

  colData <- a.colData %>%
      dplyr::filter(sextissue == eachgroup) %>%
      droplevels()
  row.names(colData) <- colData$V1

@@

  countData <- a.countData %>% dplyr::select(one_of(savecols))

@@

#dat$V1 <- factor(dat$V1, levels = 
#                              c("control", "bldg", "lay", "inc.d3", "inc.d9", 
#                                "inc.d17", "hatch", "n5", "n9",
#                                "m.inc.d3", "m.inc.d8", "m.inc.d9",
#                                "m.inc.d17",  "prolong", "extend", "m.n2"))
dat$V2 <- dat$V1
